Trending assessment for nowcasts, measurements, and forecasts

### 2024-03-06 sections/04-application.tex
Update on Overleaf.

Table~\ref{tab:app-eda-trending-ratios} lists the trending ratios for all models for three and seven-day lags.
The trending ratios range from 0.68 to 0.84 for a lag of three days and from 0.68 to 0.82 for seven days.
The negative and positive trending ratios differ for all models and lags.
For some models, for example, the GBM-2 model, the positive trending ratio is higher; for some models, for example, the tbats model, the negative trending ratio is higher.
The confidence interval width is at most 0.02 for the trending ratios and at most 0.03 for the positive and negative trending ratios.
Other models exhibit a higher positive trending ratio than the negative trending ratio.
The models GBM-2, qreg-1, and Benchmark-1 have the highest positive trending ratio for the lag of three and seven days, while Poisson-2 and NBI-2 have the highest negative trending ratio.

@@

The results of the probabilistic trending evaluation endorse the point trending assessment and assign the best scores to NBI-2 and Poisson-2. 
The reliability diagrams show that they underestimate the fraction of increases slightly. 
This aligns with the trending ratio where the

>>>>

Table~\ref{tab:app-eda-trending-ratios} lists the trending ratios for all models for three and seven-day lags.
The trending ratios range from 0.68 to 0.84 for a lag of three days and from 0.68 to 0.82 for seven days.
The negative and positive trending ratios differ for all models and lags.
For some models, for example, the GBM-2 model, the positive trending ratio is higher; for some models, for example, the tbats model, the negative trending ratio is higher.
The confidence interval width is at most 0.02 for the trending ratios and at most 0.03 for the positive and negative trending ratios.
Other models exhibit a higher positive trending ratio than the negative trending ratio.
The models GBM-2, qreg-1, and Benchmark-1 have the highest positive trending ratio for three and seven days lag, while Poisson-2 and NBI-2 have the highest negative trending ratio.

@@

The results of the probabilistic trending evaluation endorse the point trending assessment and assign the best scores to NBI-2 and Poisson-2. 
The reliability diagrams show that they underestimate the fraction of increases slightly.
